Bayesian Shape Reconstruction and Optimal Guidance for Autonomous Landing on Asteroids

### 2021-12-13 jas_response.tex
Update response

\newcommand{\norm}[1]{\ensuremath{\left\| #1 \right\|}}
\newcommand{\bracket}[1]{\ensuremath{\left[ #1 \right]}}
\newcommand{\braces}[1]{\ensuremath{\left\{ #1 \right\}}}
\newcommand{\parenth}[1]{\ensuremath{\left( #1 \right)}}
\newcommand{\pair}[1]{\ensuremath{\langle #1 \rangle}}
\newcommand{\met}[1]{\ensuremath{\langle\langle #1 \rangle\rangle}}
\newcommand{\refeqn}[1]{(\ref{eqn:#1})}
\newcommand{\reffig}[1]{Fig. \ref{fig:#1}}
\newcommand{\tr}[1]{\mathrm{tr}\ensuremath{\negthickspace\bracket{#1}}}
\newcommand{\trs}[1]{\mathrm{tr}\ensuremath{[#1]}}
\newcommand{\deriv}[2]{\ensuremath{\frac{\partial #1}{\partial #2}}}
\newcommand{\SO}{\ensuremath{\mathsf{SO(3)}}}
\newcommand{\T}{\ensuremath{\mathsf{T}}}
\renewcommand{\L}{\ensuremath{\mathsf{L}}}
\newcommand{\so}{\ensuremath{\mathfrak{so}(3)}}
\newcommand{\SE}{\ensuremath{\mathsf{SE(3)}}}
\newcommand{\se}{\ensuremath{\mathfrak{se}(3)}}
\renewcommand{\Re}{\ensuremath{\mathbb{R}}}
\newcommand{\aSE}[2]{\ensuremath{\begin{bmatrix}#1&#2\\0&1\end{bmatrix}}}
\newcommand{\ase}[2]{\ensuremath{\begin{bmatrix}#1&#2\\0&0\end{bmatrix}}}
\newcommand{\D}{\ensuremath{\mathbf{D}}}
\newcommand{\Sph}{\ensuremath{\mathsf{S}}}
\renewcommand{\S}{\Sph}
\newcommand{\J}{\ensuremath{\mathbf{J}}}
\newcommand{\Ad}{\ensuremath{\mathrm{Ad}}}
\newcommand{\intp}{\ensuremath{\mathbf{i}}}
\newcommand{\extd}{\ensuremath{\mathbf{d}}}
\newcommand{\hor}{\ensuremath{\mathrm{hor}}}
\newcommand{\ver}{\ensuremath{\mathrm{ver}}}
\newcommand{\dyn}{\ensuremath{\mathrm{dyn}}}
\newcommand{\geo}{\ensuremath{\mathrm{geo}}}
\newcommand{\Q}{\ensuremath{\mathsf{Q}}}
\newcommand{\G}{\ensuremath{\mathsf{G}}}
\newcommand{\g}{\ensuremath{\mathfrak{g}}}
\newcommand{\Hess}{\ensuremath{\mathrm{Hess}}}
\newcommand{\refprop}[1]{Proposition \ref{prop:#1}}

@@

Thanks for the comments. All of the comments have been addressed in the following response letter, and the manuscript has been revised accordingly. 
The detailed responses to each comment are given in the subsequent pages.

@@

The use of the dumbbell approximation allows use to avoid having to evaluate the integral over the extended body in the equations of motion.
The dumbbell model allows us to approximate an extended body with a miminimum of additional complexity.
Additional comments have been added to the manuscript explaining this decision and copied here.

The dumbbell is in some sense the simplest approximation of an extended rigid body.
It allows for simple analytical solution for the moment of inertia and greatly simplifies the equations of motion.
Dumbell is an approximation for a rigid spacecraft and is used widely 
Can easily extend from a dumbell, 2 masses to arbitary number of masses to handle more general spacecraft. 
In the limit an arbitrary number of masses can then approximate a general rigid body.

@@

In our analyis, we have assumed that the inertial position of both the asteroid and vehicle are available.
For both bodies we assume that ground based tracking/orbit determination is available prior to arrival.
This provides the inertial state of both bodies and is a requirement for the orbital rendezvous prior to any surface mapping operation.
Additional comments have been added to the manuscript and are repeated here.

@@

In addition, additional detail concerning spacecraft/state uncertainties and perturbing forces has been added to the manuscript.
The discussion discusses the current limitations of the presented approach and discuses this as an area of future work.
The additional discussion is presented here.

@@

@@

Depending on the specific mission objectives the preliminary mapping phase may serve multiple purposes. 
In this week, we seek to utilize the mapping phase to create a polyhedron potential model and select an appropriate landing site. 
We added additional discussion related to more recent missions and copied below.

@@

The citation to the asteroid redirect mission has been removed and additional discussion related to the OSIRIS-REX mission has been incorporated.
The additional discussion has been copied below.

@@

Onboard shape reconstruction techniques enable autonomous operations which allow for a greater range of spacecraft operations.

\comment{
Page 4 line 7, "onboard" as opposed to "onborad".
}
This typo has been corrected and is copied below.

\comment{
Page 4, line 37, "During this simulation, this update shape model is then used in a nonlinear controller...". The second "this" should not have a capital "T", and should be "used in" as opposed to "used to in" .
}
This typo has been corrected and is copied below.

@@

The polyhedron potential model is based on a triangular faceted shape model of an asteroid.
In this approach, the shape of the asteroid is used to directly compute the exterior potential.

@@

Find more recent references

@@

@@

@@

@@

@@

@@

\begin{correction}
    Areas of high uncertainty are in yellow while areas of low uncertainty are in purple.
    The guidance scheme continually selects regions of high uncertainty until the total shape uncertainty is sufficiently small.
\end{correction}

@@

\begin{correction}
    The surface cost described here is relatively simple and chosen to be solely a function of the current spacecraft position and shape model.
    Additional scientific criteria such as surface material or location on the body, e.g. equatorial vs. polar regions, can be utilized instead of a random science value as presented here.
\end{correction}

@@

\begin{correction}
This is in contrast to standard shape reconstruction algorithms which operate over the entire surface and require significant computational resources.
\end{correction}

@@

>>>>

\newcommand{\norm}[1]{\ensuremath{\left\| #1 \right\|}}
\newcommand{\bracket}[1]{\ensuremath{\left[ #1 \right]}}
\newcommand{\braces}[1]{\ensuremath{\left\{ #1 \right\}}}
\newcommand{\parenth}[1]{\ensuremath{\left( #1 \right)}}
\newcommand{\pair}[1]{\ensuremath{\langle #1 \rangle}}
\newcommand{\met}[1]{\ensuremath{\langle\langle #1 \rangle\rangle}}
\newcommand{\refeqn}[1]{(\ref{eqn:#1})}
\newcommand{\reffig}[1]{Fig. \ref{fig:#1}}
\newcommand{\tr}[1]{\mathrm{tr}\ensuremath{\negthickspace\bracket{#1}}}
\newcommand{\trs}[1]{\mathrm{tr}\ensuremath{[#1]}}
\newcommand{\deriv}[2]{\ensuremath{\frac{\partial #1}{\partial #2}}}
\newcommand{\SO}{\ensuremath{\mathsf{SO(3)}}}
\newcommand{\T}{\ensuremath{\mathsf{T}}}
\renewcommand{\L}{\ensuremath{\mathsf{L}}}
\newcommand{\so}{\ensuremath{\mathfrak{so}(3)}}
\newcommand{\SE}{\ensuremath{\mathsf{SE(3)}}}
\newcommand{\se}{\ensuremath{\mathfrak{se}(3)}}
\renewcommand{\Re}{\ensuremath{\mathbb{R}}}
\newcommand{\aSE}[2]{\ensuremath{\begin{bmatrix}#1&#2\\0&1\end{bmatrix}}}
\newcommand{\ase}[2]{\ensuremath{\begin{bmatrix}#1&#2\\0&0\end{bmatrix}}}
\newcommand{\D}{\ensuremath{\mathbf{D}}}
\newcommand{\Sph}{\ensuremath{\mathsf{S}}}
\renewcommand{\S}{\Sph}
\newcommand{\J}{\ensuremath{\mathbf{J}}}
\newcommand{\Ad}{\ensuremath{\mathrm{Ad}}}
\newcommand{\intp}{\ensuremath{\mathbf{i}}}
\newcommand{\extd}{\ensuremath{\mathbf{d}}}
\newcommand{\hor}{\ensuremath{\mathrm{hor}}}
\newcommand{\ver}{\ensuremath{\mathrm{ver}}}
\newcommand{\dyn}{\ensuremath{\mathrm{dyn}}}
\newcommand{\geo}{\ensuremath{\mathrm{geo}}}
\newcommand{\Q}{\ensuremath{\mathsf{Q}}}
\newcommand{\G}{\ensuremath{\mathsf{G}}}
\newcommand{\g}{\ensuremath{\mathfrak{g}}}
\newcommand{\Hess}{\ensuremath{\mathrm{Hess}}}
\newcommand{\refprop}[1]{Proposition \ref{prop:#1}}
\newcommand{\todo}{{\large \textcolor{red}{TODO: }}}

@@

Thanks for the comments. All of the comments have been addressed in the following response letter, and the manuscript has been revised accordingly. 
The detailed responses to each comment are given in the subsequent pages.  
As a note, reference numbers to citations or equations may not match the manuscript in this response.

@@

The primary benefit of the dumbbell approximation is to avoid the additional integral over the entire body.
While conceptually and analytically simple the dumbbell model still captures the important rigid body effects on the system, namely the coupling of attitude and translational states through the external forces and moments.
In addition, this type of spacecraft model is prevelant in the field~\cite{kulumani2017b,lee2006a,lee2007a,elmasri2005}.
Additional comments have been added to the manuscript explaining this decision and copied here.

\begin{correction}
The dumbbell model is in some sense the simplest approximation of an extended rigid body.
This model captures the important dynamics of an extended rigid body with a minmum of additional complexity and is prevelant the literature~\cite{kulumani2017b,lee2006a,lee2007a,elmasri2005}.
In addition, the developments of the dumbbell model can be trivially extended to include a larger number of discrete masses to better approximate a more complicated spacecraft model.
\end{correction}

@@

In our analyis, we have assumed that the inertial position of both the asteroid and vehicle are available prior to the mapping operations.
This data is typically available as ground based measurements are required to rendezvous with the asteroid prior to mapping.
Additional comments have been added to the manuscript and are repeated here.

\todo Add to second paragraph of Section 4.3 Numerical example immediately after the sentence: ''In other words the initial orientation is given by \( R_0 = \exp(\frac{\pi}{2} \hat e_3)\).``

\begin{correction}
    We assume that the initial intertial state of the vehicle is available. 
    This data is typically available from a ground based orbit determination scheme which enabled the original orbital rendezvous. 
\end{correction}

@@

In addition, additional detail concerning spacecraft/state uncertainties and perturbing forces has been added to the manuscript.
The discussion discusses the current limitations of the presented approach and discuses this as an area of future work.
Specific comments related to these comments have been included below.

@@

\todo Use dynamical throughout manuscript

@@

Depending on the specific mission objectives the mapping phase may serve multiple purposes, such as landing site selection or shape modelling.
In this work, we seek to utilize the mapping phase to create a shape model.
The shape model is then used for multiple purposes including the polyhedron potential model and landing site selection.
We have added additional discussion related to more recent missions and copied below.

\todo Add to introduction section - replacing the sentence: ''After arrival, a spacecraft will generally spend months or years in a mapping mission phase.``
\begin{correction}
After arrival, space will generally spend upwards of several months in a mapping mission phase~\cite{williams2018,kubota2003,cole1998}.
For example, the recent OSIRIS-REx mission used global imagery to create digital terrain maps over the span of approximately seven months~\cite{williams2018}.

\end{correction}

@@

\todo Remove citation ''gates2015`` in the introduction.

\todo add following citations~\cite{williams2018} instead.

The citation to the asteroid redirect mission has been removed and additional discussion related to the OSIRIS-REx mission has been incorporated.
The additional discussion has been copied below.

\todo Add following after sentence: ''Depending on the mission type, this long period of mapping is curicial to the mission, such as sample collection.``
\begin{correction}
For example, the OSIRIS-REx mission spent approximately seven months in mapping phase where digitial terrain maps and a shape model were constructed in support of main sample collection mission.
\end{correction}

@@

\todo Remove sentence and replace

\begin{correction}
Onboard shape reconstruction techniques enable autonomous operations which allow for a greater range of spacecraft operations.
\end{correction}

\comment{
Page 4 line 7, "onboard" as opposed to "onborad".
}

This typo has been corrected.

\todo Correct typo.

\comment{
Page 4, line 37, "During this simulation, this update shape model is then used in a nonlinear controller...". The second "this" should not have a capital "T", and should be "used in" as opposed to "used to in" .
}

\todo Correct typo
This typo has been corrected and the corrected sentence is shown below.

\begin{correction}
During this simulation, this updated shape model is then used in a nonlinear controller to track a desired state trajectory for the dynamics of a rigid body spacecraft.
\end{correction}

@@

\begin{correction}
    The sum \( \sum \omega_f \) vanishes when outside the body and equals \( -4 \pi \) inside.
\end{correction}

@@

More recent references from the OSIRIS-REx mission have been included and additional discussion is copied below.

\begin{correction}
We assume the spacecraft contains a range sensor, such as LIDAR, that allows for the accurate measurement of the relative distance between the spacecraft and asteroid~\cite{zuber1997,zuber2000}.
Recent missions such as OSIRIS-REx have featured a scanning LIDAR system which allows for much higher measurement rates compared to previous missions~\cite{lauretta2017,daly2017}.
In these mission, ranging measurements are combined with imagery to derive a shape model using a ground based method~\cite{gaskell2008}.
In constrast to previous missions, the scanning LIDAR system on OSIRIS-REx enables for high surface sample rates in spite of the low ground-track velocities~\cite{daly2017}.
\end{correction}

@@

\todo Correct the equation

\begin{correction}
    \(d = \frac{\Delta TOF c}{2} \) 
\end{correction}

@@

\todo Copy into paper after equation 19.

@@

\todo Copy into section 4.3. Either the first paragraph or a new second paragraph

@@

\todo Add to paper

@@

\todo Correct in paper

@@

\todo Correct in paper
\begin{correction}
    Areas of high uncertainty are in yellow while areas of low uncertainty are in purple.
    The guidance scheme continually selects regions of high uncertainty until the total shape uncertainty is sufficiently small.
\end{correction}

@@

\todo Correct in paper
\begin{correction}
    The surface cost described here is relatively simple and chosen to be solely a function of the current spacecraft position and shape model.
    Additional scientific criteria such as surface material or location on the body, e.g. equatorial vs. polar regions, can be utilized instead of a random science value as presented here.
\end{correction}

@@

\todo Correct in paper
\begin{correction}
This is in contrast to standard shape reconstruction algorithms which operate over the entire surface and require significant computational resources.
\end{correction}

@@

\bibliographystyle{IEEEtran}
\bibliography{library}
